Self-assembly of colloid-cholesteric composites provides a route to switchable optical materials

### 2014-02-21 papers/2012-sandwich/response.txt

The authors describe the results of a study of colloidal particles dispersed
in cholesteric blue phases (BP) focusing on the effects of particle
concentration and distribution. Additionally
effects of confinement and external fields are investigated. The use of the
lattice Boltzmann approach allows to follow dynamics after the thermal
quench and electric field application. The
study is an important step in modeling of BPs and should deserve a
publication in Nature Communications. Nevertheless there are some weak
points that need improvement before the publication.
Below is the list of remarks.

General remarks:

The term colloid is by the definition a dispersion of particles in a fluid.
Using the term also for the particles my lead to a confusion. In the
manuscript often also a more appropriate word
colloidal particle is used.

RESPONSE: We have standardised on "colloidal particle(s)" or simply
"particle(s)" where appropriate.

@@

Particular remarks:

Page 2

In the discussion of the physical understanding of trapping of colloidal
particles in BP disclination networks it would be useful to refer to the
initial study by Ravnik et al. in Faraday
Discussions 2009 devoted to this topic.

RESPONSE: Citition for Ranvik et al Faraday Discuss. 2010 (sic) is added
[current reference 16].

@@

250 K is more than the total mesophase stability range!

RESPONSE: A stability range for templated blue phases of -125 to
+125 degrees Celsius is reported by Castles et al. Nat. Mat. 2012.
We have made this connection more clear by rewriting the relevant
sentence: "However, recent advances in formalation have widened
this stability range enormously [11,12,13,14]. Most recently,
templated blue phases with a stability range of -125 to 125$^\circ$C
have been reported [Castles], paving the way to applications of BPs
in operational display devices."

@@

Page 3

The statement "This is defined such that W > 0 gives preferential
perpendicular orientation of the director field at the particle surface." is
not consistent with the interaction form
described in the Supplement.

RESPONSE: We agree this statement is confusing. It has been replaced by
a clearer statement: "The anchoring strength is defined such that
W > 0 imparts a preferred orientation to the director field at the
particle surface. This orientation can be either normal to the
surface or in a plane tengential to the surface, a property related
to surface chemistry in experimental systems but which can be imposed
at will in simulations."

@@

For potential readers it would be useful to specify the particle radius in
nanometers in the main text. How it compares to the nematic correlation
length? How the radius influences the
structures? How tiny the particles can still be that the method based on the
Landau-de Gennes free energy is justified.

Is WR/K = 2.8 justified for nanoparticles used in the study?

RESPONSE: We have added in the main text (last para. introduction) a
summary of the relevant
dimensions in physical units: "The simulations represent a liquid crystal
blue phase with unit cell size in the range of 100--500~nm \cite{mermin},
and particles with a radius of around 50~nm."

...

@@

Can annealing of the structures obtained with the thermal quench lead to
ordered colloidal structures?

Is also in case of the disordered structures observed a change in the
stability range of the colloidal BPs?

In the discussion of colloidal particles in BP thin layers it would be good
to comment the study of
Ravnik et al. in Soft Matter 2011 devoted the ordered structures of such a
system.

REESPONSE: A citition for Ravnik et al (2011) has been added [current
reference 26].

@@

Are the electric field induced changes irreversible only in case of
colloidal dispersions?

Page 7

Reference 2 has a mistake.

RESPONSE: The corrent punctuation in the page numbers has been
inserted in the reference for Wright and Mermin [current reference 9].

@@

Supplement

Segment 4.2:

The statement "Wall anchoring is either normal or planar with W=K = 1 in
simulation units" is unclear.

RESPONSE: This text has been replaced by a statement which is
transparent: "For both normal and planar anchoring at the walls,
values of $W$ and $K$ are used which are the same as for the
strongly anchoring particles."

@@

References of the Supplement:
There are mistakes in references 1 and 2.

REPSONSE: Reference 1, Wright and Mermin, was correct in
the original supplement. Reference 2 has been updated to reflect
the 2nd edition of de Gennes and Prost, which now appears in the
main text [current reference 33].

@@

The paper builds on a body of previous research, both theoretical and
experimental that has explored the effects of dispersing particles in a
liquid crystal host. The novelty of the paper is
to model the effect of particles in the blue phases of a cholesteric host
ahd to postulate how these colloids may be employed in specific
appilcations.

I am not a theorteical physiscist and therefore will not comment on the
methodology but rather will take the perspective of an experimentalist and
how useful this paper is in understanding
these materials and more importantly how useful the paper is in suggesting
and designing experimental procedures and developing the actual materials.

The paper provides insight into the effectiveness of including particles
into the blue phase as a means of controlling and adjusting the structure
and stability of the materials. The paper
is clearly written and the figures, paricularly the included 3D videos,
provide clear perspective on the modeled phases of these materials. The
results are of interest and useful to
experimentalists working in the field. The paper would be even more useful
if it included references to actual materials, both the liquid crystal host
and the added particles and perhaps
even suggested a model system that would be a good starting point to study
experimentally. In a similar vein, it would also be useful to address the
practical issue of reproducibility, which
has been a major problem with these materials. The theoretical results
clearly indicate how important the formation conditions are to the final
result. What is the authors sense of how easy
it will be to reproducibly fabricate a device
with a specific morphology and optical properties. This seems a likely
practical issue particularly with the rich variety of structures reported in
the simulations.

* ADDITIONAL CHANGES TO MEET FORMAT REQUIREMENTS

A number of other rearrangements have taken place to meet the
format requirements as set out the manuscript checklist.

Title

- The title has been adjusted to remove punctuation

Authors

- The full postal address has been added
- The corresponding author has been identified (Marenduzzo).

Abstract

- The abstract has been shorted to meet the 150 word limit.
  Citations have been removed to the main text.

Main text

- Symbols and units have been adjusted in places to come into style.

Results

- Subheadings of < 60 characters have been added

- References to supplementary items have been adjusted to come into style.

Methods

- All "methods" material (originally in supplementary information) is now
contained within the main paper. This includes relevant references.

- Dividing subheadings of < 60 characters have been added.

References

- Formatting is adjusted to come into style.

End notes

- A statement of author contributions has been added.

- A statement on conflicts of interest has been added.

Legends

- Figure legends have been adjusted to include a brief title.

Tables

- A title has been included.
